%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{RedTech Recruitment Ltd}{}
\date{March 01, 2024}
\opening{Dear Mr. Bull,}
\closing{Sincerely,}
\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

I am writing to express my interest in the Application Software Engineer - JavaScript position advertised on Milkround, with reference ID: ASER01. As a dedicated AI/ML Engineer with a strong foundation in JavaScript, Node.js, and a passion for web technologies, I am excited about the opportunity to contribute to the team.

During my tenure as a Senior Software Engineer at Tiatech Health Technologies and a Part-Time Research Assistant at the University of Cambridge, I honed my skills in JavaScript, Node.js, and various other web technologies. I spearheaded projects that enhanced product UI/UX and implemented innovative solutions in digital manufacturing, showcasing my ability to rapidly adapt to new technologies and frameworks. My academic pursuits, including an MSc in Artificial Intelligence from the University of Surrey, have equipped me with a deep understanding of the technical aspects and ethical considerations in AI applications, further enriching my software development skills.

I am particularly drawn to this role because of its focus on using a diverse toolset to work on web application infrastructure projects. My experience in developing, deploying, and maintaining web application infrastructure, along with my proactive approach to learning and adaptability, aligns perfectly with the responsibilities outlined for this position. I am eager to bring my background in both AI/ML and web development to your team, contributing to innovative solutions and the continuous improvement of your web applications.

I am enthusiastic about the opportunity to discuss how my education, skills, and experiences align with the needs of your team. I am looking forward to the possibility of contributing to your projects as an Application Software Engineer and am available at your convenience for an interview.

Thank you for considering my application. I am looking forward to the opportunity to discuss my application in further detail.

\makeletterclosing
