% possible options include font size ('10pt', '11pt' and '12pt'), 
% paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape')
% and font family ('sans' and 'roman')
\documentclass[11pt,a4paper,sans]{moderncv}

% style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvstyle{classic}
% color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
\moderncvcolor{blue}
% to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
% \renewcommand{\familydefault}{\sfdefault}
% uncomment to suppress automatic page numbering for CVs longer than one page
% \nopagenumbers{}

% adjust the page margins
\usepackage[scale=0.85]{geometry}
% depending on the amount of information in the footer, you need to change this value.
% comment this line out and set it to the size given in the warning
\setlength{\footskip}{136.00005pt}
% if you want to change the width of the column with the dates
% \setlength{\hintscolumnwidth}{3cm}
% for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
% \setlength{\makecvheadnamewidth}{10cm}

% font loading
% for luatex and xetex, do not use inputenc and fontenc
% see https://tex.stackexchange.com/a/496643
\ifxetexorluatex
  \usepackage{fontspec}
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont{Latin Modern Roman}
  \setsansfont{Latin Modern Sans}
  \setmonofont{Latin Modern Mono}
  \setmathfont{Latin Modern Math} 
\else
  \usepackage[T1]{fontenc}
  \usepackage{lmodern}
\fi

% document language
% FIXME: using spanish breaks moderncv
\usepackage[english]{babel}

% personal data
\name{Rohit}{Krishnan}
\title{AI/ML Engineer}
% \born{17 October 2000}
% the "postcode city" and "country" arguments can be omitted or provided empty
% \address{street and number}{postcode city}{country}
% the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\phone[mobile]{+44 7874 368066}
% \phone[mobile]{+91 6238 324146}
\email{rohit.k.kesavan@gmail.com}
\homepage{rohitkrishnan-com.vercel.app}

% Social icons
\social[linkedin]{rohit-krishnan25}
\social[github]{Cogniveon}
% \social[stackoverflow]{0000000/johndoe}
% \social[bitbucket]{jdoe}
% \social[skype]{jdoe}
% \social[orcid]{0000-0000-000-000}
% \social[researchgate]{jdoe}
% \social[researcherid]{jdoe}
% \social[telegram]{jdoe}
% \social[whatsapp]{12345678901}
% \social[signal]{12345678901}
% \social[matrix]{@johndoe:matrix.org}
% \social[googlescholar]{googlescholarid}


% \extrainfo{additional information}
% '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it 
% (put it to 0pt for no frame) and 'picture' is the name of the image file
% \photo[64pt][0.4pt]{picture}
% \quote{}

% bibliography adjustments (only useful if you make citations in your resume, or print a list of publications using BibTeX)
% to show numerical labels in the bibliography (default is to show no labels)
% \makeatletter\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}\makeatother
\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}
% to redefine the bibliography heading string ("Publications")
% \renewcommand{\refname}{Articles}

% bibliography with mutiple entries
% \usepackage{multibib}
% \newcites{book,misc}{{Books},{Others}}


\begin{document}
\input{glyphtounicode}
\pdfgentounicode=1
% to typeset your resume in Chinese using CJK
% \begin{CJK*}{UTF8}{gbsn}

% \include{cover_letter}

% CV begins here...
\makecvtitle

\section{Profile}

% I am a dedicated AI/ML engineer who loves to throw himself at challenging problems and find results. I am currently
% a full time student, studying MSc Artificial Intelligence at the University of Surrey. I enjoy building software as
% a team and I am always looking for ways to improve my skills. I am extremely quick to grasp new
% concepts and understand how new technologies work, I often perform the most when required to explore and develop
% new features for projects I work on.

A dedicated and dynamic AI/ML Engineer, I am currently enriching my expertise through an MSc in Artificial Intelligence
at the University of Surrey. My academic and professional journey is marked by a strong commitment to tackling complex
challenges and delivering innovative solutions. Specialized in various web-technologies and AI, I excel in not only
grasping new technologies rapidly but also in applying them effectively in project environments.

My collaborative spirit stands out as I enjoy contributing to team efforts and continuously seek avenues for skill
enhancement. This blend of technical prowess, proactive approach to learning and adaptability positions me
uniquely for roles that require both the depth and breadth in Computer Vision and Machine Learning.

\section{Experience}
\cventry{Oct 2023 -- Present}{Part-Time Research Assistant}{University of Cambridge}{Remote}{}{
\begin{itemize}
  \item Contributing to innovative projects in Digital Manufacturing \& Infrastructure Digital Twins
\item Demonstrated ability to combine theoretical knowledge with hands-on experience.
\item Key contributions:
\begin{itemize}
\item Developed a sample tracking solution for a histopathology lab, addressing the challenge of enhancing label visibility in images through preprocessing with OpenCV. Employed fine-tuned and pre-trained CNN models (YOLOv8) to extract precise bounding boxes around sample labels, and applied OCR (Optical Character Recognition) to extract vital sample information from these labels, streamlining the sample tracking process.
\item Optimized and containerized machine learning models (using Docker and Python), enabling their efficient deployment on Raspberry Pi microcontrollers.
\item Maintained a React-based frontend that effectively visualizes the digital twin of a hospital for enhanced operational insight and management.
\end{itemize}
\end{itemize}
  % General description no longer than 1--2 lines.\newline{}
  % Detailed achievements:
  % \begin{itemize}
  %   \item Achievement 1
  %   \item Achievement 2 (with sub-achievements)
  %         \begin{itemize}
  %           \item Sub-achievement (a);
  %           \item Sub-achievement (b), with sub-sub-achievements (don't do this!);
  %                 \begin{itemize}
  %                   \item Sub-sub-achievement i;
  %                   \item Sub-sub-achievement ii;
  %                   \item Sub-sub-achievement iii;
  %                 \end{itemize}
  %           \item Sub-achievement (c);
  %         \end{itemize}
  %   \item Achievement 3
  %   \item Achievement 4
  % \end{itemize}
}
\cventry{May 2022 -- Jul 2023}{Senior Software Engineer}{Tiatech Health Technologies}{Thrissur}{}{
\begin{itemize}
  \item Commenced my career journey at Tiatech as a Software Engineering Trainee, demonstrating exceptional skills and dedication by transforming "TiaImage," a radiology image viewer, impressing both company stakeholders and clients with the enhanced product UI/UX which resulted in a rapid promotion to Senior Software Engineer within just 3 months.
  \item I was assigned to a dynamic 5-member team in the development of Python microservices, widely adopted by more than 30 hospitals for DICOM imaging and analysis, as well as teleconferencing solutions for collaborative consultations over the internet.
  \item Conducted thorough research and implemented necessary modifications to ensure compliance with ONC certification for US markets, effectively meeting the stringent g10 and c1 certification criteria, further solidifying the company's commitment to quality and regulatory standards.
\end{itemize}
}
\cventry{July 2019 -- August 2019}{Summer Intern}{Jaldee Soft Pvt Ltd}{Thrissur}{}{
\begin{itemize}
  \item Successfully completed a Summer Internship at Jaldee Soft Pvt Ltd, where I played a pivotal role in developing well-tested services for an Angular frontend to communicate with a Java Spring Boot backend.
  \item Worked collaboratively with the team, utilizing Agile methodologies with Jira for efficient project management, and embraced Test-Driven Development (TDD) principles to ensure code quality and maintainability.
  \item Gained invaluable hands-on experience early in my career, enhancing my software development skills and contributing to real-world projects.
\end{itemize}
}

\newpage{}

\section{Education}
% arguments 3 to 6 can be left empty
\cventry{2023--Present}{MSc Artificial Intelligence}{University of Surrey}{Guildford}{}{
  \begin{itemize}
\item Specialization in Computer Vision, Deep Learning and Natural Language Processing
\item Gained a robust understanding of machine learning fundamentals and the importance of ethical considerations in AI applications
  \end{itemize}
}
\cventry{2018--2022}{Bachelor of Technology in Computer Science}{Neusoft Institute of Technology}{Guangdong}{}{
  \begin{itemize}
    \item Achieved a high GPA of 3.94, reflecting consistent dedication to my studies. Recognized as one of the top
          performers in my batch, evidencing my strong commitment to excellence in the field of computer science.
    \item Bachelor thesis on a serverless e-commerce platform to evaluate how small-scale businesses can maintain
          cost-effective online operations.
    \item Excelled in key courses such as:
          \begin{itemize}
            \item Fundamentals of Programming (Java): Scored 100/100
            \item Data Structures and Algorithms: Scored 92/100
          \end{itemize}
  \end{itemize}
}

\section{Projects}
\cvitem{Title}{\textbf{Knife classification in real-world images}}
% \cvitem{Supervisors}{Prof. Xiatian Zhu}
\cvitem{Description}{
  Designed a custom convolutional neural network and studied the impact of various hyper-parameters on a fine-grained
  classification problem as part of my coursework for my masters at University of Surrey.
}

\cvitem{Title}{\textbf{Digital Manufacturing on a Shoestring}}
% \cvitem{Supervisors}{Prof. Ajith Kumar Parlikad}
\cvitem{Description}{
  Hands-on experience at the University of Cambridge, where I participated in successfully deploying modularized
  components of the Shoestring architecture, showcasing expertise in Docker and Python scripting for streamlined
  and low-cost digital manufacturing implementations.
}

\cvitem{Title}{\textbf{Infrastructure Digital Twins}}
% \cvitem{Supervisors}{Prof. Ajith Kumar Parlikad}
\cvitem{Description}{
  Implemented sample tracking solutions for a histopathology lab as a research assistant at the University of
  Cambridge by leveraging computer vision and machine learning techniques, enhancing efficiency and accuracy in
  sample management.
}

\section{Skills}
\cvitem{Languages}{Python, Java, JavaScript/TS, Rust, C, Scala, PHP}
\cvitem{$\mu$ Controllers}{ESP32-S2 and later, RP2040, nRF54, STM32 series}
\cvitem{Frameworks}{
  PyTorch, YOLO (ultralytics), Scikit-learn, NextJS (React.js framework), Angular, Django, FastAPI, Spring boot,
  Laravel, React Native, VueJS, PySide (QT Framework),
  JavaFX, OpenGL, ESP-IDF
}
\cvitem{Databases}{PostgreSQL, MongoDB, DynamoDB, Redis, InfluxDB, MySQL}
\cvitem{Cloud/Tools}{AWS, GCP, Figma, Docker, Kubernetes, Git/Gitlab (automation and versioning), JIRA}
\cvitem{Soft-skills}{Hardworking, Excellent Communication skills, Positive and ready-to-learn mindset}

\section{Honor and Awards}

\cvitem{2022}{
  Excellent Graduate Award for academic and athletics performance during my bachelors.
}
\cvitem{2018}{Ranked first in 12th Grade Computer Science \(98\%\)}
\cvitem{2017}{
  Voted as the School Agni House Captain. Played a major role in orchestrating team activities and fostering a
  competitive and collaborative environment among students.
}
\cvitem{2016}{Ranked first in 10th Grade Computer Science \(99\%\) and French}

\section{Languages}
\cvdoubleitem{English:}{Native or Bilingual proficiency}{Hindi:}{Native or Bilingual proficiency}
\cvdoubleitem{Japanese:}{Beginner proficiency}{Mandarin:}{Beginner proficiency}


\clearpage

% if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly
% with CJK, though it kills the page numbering by making \lastpage undefined
% \end{CJK*}

\end{document}
